---
title: "Weight of Fish"
author: "Carmen Ramos-Caminos"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)

Fish = read.csv("Fish.csv")
Perch = filter(Fish, Species == "Perch")
Pike = filter(Fish, Species == "Pike")
Roach = filter(Fish, Species == "Roach")
```

# Predicting Fish Weight

## Perch
```{r}

pwt = lm(Weight~ Length1+ Length2+ Length3+ Height, data =  Perch)
summary(pwt)
```
```{r}
library(leaps)
regsubsets.out <-
regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
data = Perch,
nbest = 2, # 1 best model for each number of predictors
nvmax = NULL, # NULL for no limit on number of variables
force.in = NULL, force.out = NULL,
method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```
From this graph I conclude that the best two predictors of weight for Perch are Height and length3.

### Best Models
The best model for this case is using all 4 variables

### Best Two regressor model
From this graph I conclude that the best two predictors of weight for Perch are Height and length3.

## Pike

```{r}

pwt = lm(Weight~ Length1+ Length2+ Length3+ Height, data =  Pike)
summary(pwt)
```
```{r}
library(leaps)
regsubsets.out <-
regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
data = Pike,
nbest = 2, # 1 best model for each number of predictors
nvmax = NULL, # NULL for no limit on number of variables
force.in = NULL, force.out = NULL,
method = "exhaustive")
regsubsets.out
```
```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

### Best Models

### Best Two regressor model






## Roach

```{r}

pwt = lm(Weight~ Length1+ Length2+ Length3+ Height, data =  Roach)
summary(pwt)
```
```{r}
library(leaps)
regsubsets.out <-
regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
data = Roach,
nbest = 2, # 1 best model for each number of predictors
nvmax = NULL, # NULL for no limit on number of variables
force.in = NULL, force.out = NULL,
method = "exhaustive")
regsubsets.out
```
```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

### Best Models

### Best Two regressor model




## Final Summary Statements